%----------------------------------------------------------------------------------------
%	CONFIGURATION
%----------------------------------------------------------------------------------------

\documentclass[10pt]{developercv}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	CONTACT DETAILS
%----------------------------------------------------------------------------------------
\begin{minipage}[t]{0.45\textwidth}
	\vspace{-\baselineskip}
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Giorgos}}}}}
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Kalmoukis}}}}}
	\vspace{6pt}
	{\huge Software Engineer}
\end{minipage}
\begin{minipage}[t]{0.275\textwidth}
	\vspace{-\baselineskip}
	\icon{MapMarker}{12}{Athens, Greece}\\
	\icon{Phone}{12}{\href{tel:+306936750072}{+30 693 675 0072}}\\
	\icon{At}{12}{\href{mailto:hi@gkalmoukis.com}{hi@gkalmoukis.com}}\\	
\end{minipage}
\begin{minipage}[t]{0.345\textwidth}
	\vspace{-\baselineskip}
	\icon{Globe}{12}{\href{https://gkalmoukis.com}{gkalmoukis.com}}\\
	\icon{Github}{12}{\href{https://github.com/gkalmoukis}{github.com/gkalmoukis}}\\
	\icon{Linkedin}{12}{\href{https://www.linkedin.com/in/gkalmoukis}{linkedin.com/in/gkalmoukis}}\\
\end{minipage}
\vspace{0.5cm}
%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------
\cvsect{Who Am I?}

\begin{minipage}[t]{0.4\textwidth}
	\vspace{-\baselineskip}
	I'm Giorgos Kalmoukis, and I love teamwork, fixing things, and using open ways of doing stuff. I've enjoyed coding with PHP, and I'm experienced with MVC frameworks like Symfony and Laravel. Additionally, I've worked with JavaScript and the Nuxt framework. Currently, I'm a Back-end developer at a digital agency. I'm excited to learn new ways of making software.\\
\end{minipage}
\hfill
\begin{minipage}[t]{0.5\textwidth}
	\vspace{-\baselineskip}
	\begin{barchart}{5.5}
		\baritem{JavaScript}{50}
		\baritem{PHP}{80}
		\baritem{Git}{70}
		\baritem{Java}{30}
		\baritem{Python}{30}
		\baritem{MySQL}{70}
	\end{barchart}
\end{minipage}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Experience}

\begin{entrylist}
	\entry
		{09/2020 - now}
		{Back-end Software Engineer}
		{HappyOnline, Athens}
		{As Back-End Developer, I lead a team in crafting custom web applications in domains including Learning Platforms, Risk Management Appl, Booking Engines, Marketing Platforms, Custom CMS, and Fintech Applications. Leveraging Laravel, I spearhead the development of these solutions, enhancing existing ones and creating new ones. \\ \texttt{Laravel}\slashsep\texttt{Symfony}\slashsep\texttt{JavaScript}\slashsep\texttt{Nuxt}}
	\entry
		{02/2019 - 09/2020}
		{Back-end Software Engineer}
		{Pockee, Athens}
		{My main responsibility in this project was to build and maintain a web scraping micro-service for searching prices and oers from retailers. Besides that, I participated in the development process of the existing FMCG market tools like a loyalty system for customers, OCR handlers, and orders classication. \\ \texttt{Laravel}\slashsep\texttt{Symfony}\slashsep\texttt{JavaScript}\slashsep\texttt{ELK}}
	\entry
		{2017 - 2018}
		{Back-End Web Developer}
		{Vela Digital, Athens}
		{Being part of a web agency team as a Back-End developer building custom made web applications, mainly in the tourism industry.\\ \texttt{WordPress API}\slashsep\texttt{Laravel}\slashsep\texttt{OpenCart}}
	\entry
		{2017 - 2019\\\footnotesize{Freelancing}}
		{Full-Stack Web Developer}
		{Apollo Parking Facilities, Athens}
		{I participated as a full-stack developer in the design and development process of the web application for an online car rental system.\\ \texttt{PHP}\slashsep\texttt{JavaScript}\slashsep\texttt{MySQL}}
	\entry
		{2017 - 2018}
		{Back-End Web Developer}
		{Travelgems, Athens}
		{Designing and developing a SaaS recommendation engine using the programming language Java. Consulting on the back-end infrastructure.\\ \texttt{Java EE}\slashsep\texttt{MySQL}\slashsep\texttt{Apache Tomcat} }
	\entry
		{2016 - 2017\\ \footnotesize{Internship}}
		{Software Support Engineer}
		{Siveco, Athens}
		{Audit, and maintain business processes. Provide technical assistance and support for CMMS software. Perform troubleshooting on issues from IT users. Build custom reports using Crystal reports.\\ \texttt{Java EE}\slashsep\texttt{SQL Server}\slashsep\texttt{Oracle Database}}
	\entry
		{05 - 10/2015\\ \footnotesize{Volunteer}}
		{IT Department}
		{Laiko General Athens Hospital}
		{I was learning about Computer networking and Server maintenance in a large organization.}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{Education}

\begin{entrylist}
	\entry
		{2011 - 2016}
		{Studied Informatics and Telecommunications}
		{University of Ioannina, Greece}
		{}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip}
	\cvsect{Languages}
	\textbf{Greek} - native\\
	\textbf{English} - fluent\\
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip}
	\cvsect{TECK STACK}
	\textbf{PHP}\\
	\textbf{JavaScript}\\
	\textbf{Nuxt}\\
	\textbf{GIT}\\
	\textbf{Jenkins}\\
	\textbf{Docker}\\
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip}	
	\cvsect{FYI}
	Travel, arts and juggling
\end{minipage}

%----------------------------------------------------------------------------------------

\end{document}